API design for machine learning software: experiences from the scikit-learn project

### 2013-06-26 paper.tex
Cosmit.

From its core, the library has been designed to tie in with the set of numeric
and scientific packages centered around the NumPy and SciPy libraries. NumPy
\citep{vanderwalt2011} augments Python with a numeric array data type and proper
array computing primitives, while SciPy \citep{varoquaux2013scipy} extends it
further by making common numerical operations available, either by implementing
these in Python/NumPy or by wrapping existing C/C{}\verb!++!/Fortran
implementations. The \textit{scikits} were created to complement SciPy with
domain-specific toolkits. Currently, the two most popular and feature-complete
ones are by far \sklearn and 
\textit{scikit-image}\footnote{\url{http://scikit-image.org}}, an
image-processing library.

>>>>

From its core, the library has been designed to tie in with the set of numeric
and scientific packages centered around the NumPy and SciPy libraries. NumPy
\citep{vanderwalt2011} augments Python with a numeric array data type and proper
array computing primitives, while SciPy \citep{varoquaux2013scipy} extends it
further by making common numerical operations available, either by implementing
these in Python/NumPy or by wrapping existing C/C{}\verb!++!/Fortran
implementations. The \textit{scikits} were created to complement SciPy with
domain-specific toolkits. Currently, the two most popular and feature-complete
ones are by far \sklearn for machine learning and 
\textit{scikit-image}\footnote{\url{http://scikit-image.org}} for image
processing.
